Managing IoT Devices with LwM2M

### 2024-11-12 paper.tex
incorporated sandor's feedback

@@

We would like to thank Ericsson for their support of this work. Special thanks to Jari Arkko and Carsten Bormann for their valuable review and feedback, which improved the quality of this paper.

>>>>

The evolution of LwM2M has also prompted considerations for enhancing its data model capabilities. While the current IPSO data model, utilizing the format \textit{/<ObjectID>/<InstanceID>/<ResourceID>}, is well-suited for constrained environments, it may fall short in addressing the needs of complex machines or network nodes with large, deeply nested configuration structures. This limitation suggests the potential for developing alternative data models that can accommodate more intricate configurations, thereby extending the LwM2M protocol's applicability to a broader range of devices.

The interoperability of LwM2M with hyperscalers is hindered by the lack of native CoAP support within these platforms. This limitation poses a challenge for vendors seeking to integrate LwM2M-based IoT solutions with HCS services. To overcome this obstacle, some vendors have devised methods to encapsulate CoAP messages within MQTT topics, although this solution is merely a workaround that may not fully address the efficiency needs of large-scale IoT deployments.

@@

We would like to thank Ericsson for their support of this work. Special thanks to Jari Arkko, Carsten Bormann and Sándor Katona for their valuable review and feedback, which improved the quality of this paper.
